%
% Copyright © 2016 Peeter Joot.  All Rights Reserved.
% Licenced as described in the file LICENSE under the root directory of this GIT repository.
%

%
%\chapter{Preface}
% this suppresses an explicit chapter number for the preface.
\chapter*{Preface}%\normalsize
  \thispagestyle{empty}
  \addcontentsline{toc}{chapter}{Preface}

This document was produced while taking the Fall 2016, University of Toronto
Electromagnetic Theory
course (ECE1228H), taught by Prof.\ M. Mojahedi.

\paragraph{Course Syllabus.}
This course was an introduction to the fundamentals of electromagnetic theory, with the following syllabus topics
\begin{itemize}
\item Maxwell's equations
\item constitutive relations and boundary conditions
\item wave polarization.
\item Field representations: potentials
\item Green's functions and integral equations.
\item Theorems and concepts: duality, uniqueness, images, equivalence, reciprocity and Babinet's principles.
\item Plane cylindrical and spherical waves and waveguides.
\item radiation and scattering.
\end{itemize}

\withproblemsetsMessage{
\textcolor{Maroon}{
\textit{THIS DOCUMENT IS REDACTED.  THE PROBLEM SET SOLUTIONS ARE NOT VISIBLE.  PLEASE EMAIL ME FOR THE FULL VERSION IF YOU ARE NOT TAKING ECE1228.}
}
}
\paragraph{This document contains:}
\begin{itemize}
\item Lecture notes (or transcriptions from the class slides when they went too fast).
\item Personal notes exploring auxiliary details.
\item Worked practice problems.
\ifthenelse{\boolean{redacted}}%
{%
\item Links to Mathematica notebooks associated with the course material and problems (but not problem sets).
}%
{
\item Assigned problems.%
\item Links to Mathematica notebooks associated with problems and course material.%
}
\end{itemize}

My thanks go to Professor Mojahedi for teaching this course.

Peeter Joot  \quad peeterjoot@pm.me
